FictionEro - Affective Impact of Fiction

### 2025-07-17 study1/analysis/2_emotions.qmd
updated script

```{r}
m_arousal <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / Condition + 
                                (Relevance | Participant) + (1|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

>>>>

```{r}
m_arousal <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / Condition + 
                                (Relevance | Participant) + ((Relevance / Condition)|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
